Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-29 thesis/paper/thesis.tex
law 1

\section{RQ2 Lehman}

\subsection{1 Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}

Their partners are good at solving problems, so anything lacking from the API was solved, but in a way that they didn’t not think was a good way.

Overall the impression given suggested that it is important to improve the APIs. She even told us that some partners had requested more frequent updates to include or add new features to the API.

@@

%%William add conclusion ideas here

>>>>

\section{RQ2 Lehman}
This section will present results related to \textbf{RQ2}. The information introduced was collected during the interview with the case company.

\subsection{1 Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
From the information that was gathered in the interviews, we can conclude that Law \# 1 is holds for APIs. The case company described that including new functional content was one of the top priorities for the 2.0 release. It was also mentioned that the API users had previously reqeusted more frequent updates to the API, despite the drawbacks this could have. One of the main reasons for continuously adapting the API is also to force (!!!wording) the API users to use the API in the way that it is intended. Previously, many applications which worked around the lacking (!!!negative wording) functionality had been developed. These applications were fully functional, but were developed very differently from user to user (!!!wording).

@@

%%William add conclusion ideas here
It's interesting that the partners have mentioned that they want more frequent updates... maybe API developers should be less afraid of updating them?
